---
title: "Lab5"
author: "Lingchen Lou"
date: 'Due noon October 17, 2018'
output:
  pdf_document:
    fig_height: 4
    fig_width: 7
---

## 1) Suppose you are betting that you get at least one six in 4 throws of a die.Write a function that simulates one round of the game and prints out whether you win or lose.

```{r}
dice = c(1:6)
win=0
game <- function(N) {
  for(i in seq_len(N)) {
    x = sample(dice, size = 4, replace=TRUE)
    if(6 %in% x ) {
      win = win + 1
    }
  }
  prop = round(win / N, 4)
  return(prop)
}

game(1000)
game(10000)
```

## 2) Write a function that will find the smallest element of a given vector (built-in min() is not allowed). Your function should return the smallest element and index of the smallest element.Ex. vector is (1, 4, 2, 0, 5), then the smallest element - 0 and index is 4.
```{r}

MinInd <- function(x){
min= x[1]
index=1
  if(length(x)>1){
    for(i in 2:length(x)){
      if(x[i]<min){
        min = x[i]
        index = i
      }
    }
  }
print(paste("Minimun is", min))
print(paste("Index:",c( which(x %in% c(min)))))

}

MinInd(c(1, 4, 2, 0, 5))
MinInd (c(1,7,1,0,9,0,2))

```







